\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{1.0\textwidth}[t]{@{\extracolsep{\fill}}l@{}r}
    \textbf{#1} & \textbf{\small #2} \\
    \textit{\small#3} &  \\
    \textit{\small #4} & \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheadingExp}[3]{
  \vspace{-2pt}\item
  \begin{tabular*}{1.0\textwidth}[t]{@{\extracolsep{\fill}}l@{}r}
    \textbf{#1} & \textbf{\small #2} \\
    \textit{\small #3} & \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{0.5em}}r}
        \small #1 | \textbf{\small \underline{\href{#2}{Github}}}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeadingOS}[1]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{0.5em}}r}
        \small#1\\
    \end{tabular*}\vspace{-7pt}
}



\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Swayam Agrawal} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +91 9725482268 ~ \href{mailto:swayamagrawal1004@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{swayamagrawal1004@gmail.com}} ~ 
    \href{https://linkedin.com/in/swayam-agrawal-8ab913234/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/swayamagrawal}}  ~
    \href{https://github.com/schlechter-afk}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/schlechter-afk}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {International Institute of Information Technology, Hyderabad}{Expected May 2025}
      {B.Tech. (Honours) in Computer Science and Engineering: CGPA - 9.13/10.0}
      {Undergraduate Researcher at Robotics Research Center (RRC) working in SLAM Algorithm thread}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheadingExp
      {Zam Engg and Logistics Pvt Ltd.}{January 2023 -- April 2023}
      {Software Engineer Intern}
      \resumeItemListStart
        \resumeItem{Development of Hire Truck, a full stack application aimed at connecting freight owners and truck owners to optimize resource utilization and reduce fuel wastage. The platform leveraged the MERN stack and incorporated essential security measures to protect user information through the use of JWT (JSON Web Tokens).}
        \resumeItem{Created an intuitive map view feature using the OpenStreetMap API, allowing users to visualize their source and destination addresses with marked locations.Utilized the Bing Distance Matrix API to calculate distances accurately, facilitating efficient route planning and cost optimization.
        }
        \resumeItem{Developed and implemented a matching algorithm within the application to analyze various parameters, such as location, availability, and cargo requirements, to suggest the best matches for both freight owners and truck owners.}
        \resumeItem{Streamlined the user experience through an intuitive and easy-to-use interface, enabling users to access the platform effortlessly.}
        \resumeItem{Demonstrated strong teamwork skills by actively contributing to the majority of the project's development work. Communicated and coordinated effectively with team members to ensure seamless integration of individual contributions.}
      \resumeItemListEnd  
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{ChatterBox} $|$ \emph{MongoDB, ExpressJS, ReactJS, NodeJS, ChartJS, Docker, Nginx, SocketIO, ImageKit}} {https://github.com/schlechter-afk/ChatterBox}
          \resumeItemListStart
            \resumeItem{Developed a fully functional dockerized web application called Greddit inspired by Reddit, using MERN stack.}
            \resumeItem{Implemented features such as user registration, authentication, posting, commenting, and upvoting/downvoting functionality, moderator privileges, banned keywords, realtime chat, image uploading, notification system, charts demonstrating traffic on subreddits etc.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Extended COC} $|$ \emph{Python, OOPS, UnitTesting}}{https://github.com/schlechter-afk/RuneReign}
          \resumeItemListStart
            \resumeItem{Extended an existing Clash of Clans game by adding features such as special attack and movements. Wrote a test script using UnitTest module to test two of the features implemented demonstrating unit testing.}
          \resumeItemListEnd 
          \vspace{-13pt}
        \resumeProjectHeading
          {\textbf{Society Management System} $|$ \emph{Python, SQL}}{https://github.com/schlechter-afk/HabitatHQ}
          \resumeItemListStart
            \resumeItem{Collaboratively developed a society management system as a CLI using Python and MySQL (pymysql library) to access a SQL database containing all the relevant details of a household society.}
          \resumeItemListEnd 
          \vspace{-13pt}
        \resumeProjectHeading
          {\textbf{Water Flow Monitoring System} $|$ \emph{HTML, Bootstrap CSS, JavaScript, PHP }}{https://github.com/schlechter-afk/AquaLytix}
          \resumeItemListStart
            \resumeItem{Collaboratively developed a website creatively styled using Bootstrap created for data analysis and display of water flow rates through meaningful graphs using ChartJS.}
          \resumeItemListEnd  
            \vspace{-13pt}
        \resumeProjectHeading
          {\textbf{CF Stalker} $|$ \emph{ExpressJS}}{https://github.com/schlechter-afk/AquaLytix}
          \resumeItemListStart
            \resumeItem{Collaboratively developed a Codeforces profile tracking application such that one can now see the progress of any user of the coding platform and get problems solved by them filtered by tags, rating, educational etc. using Codeforces API.}
          \resumeItemListEnd  
        \vspace{-13pt}
        \resumeProjectHeading
          {\textbf{SWiShell} $|$ \emph{Makefile, C, Git, Operating System Concepts}}{https://github.com/schlechter-afk/SWiSH}
          \resumeItemListStart
            \resumeItem{Implemented a linux-styled terminal (shell) in C from scratch. Features/Commands included are: command pipelines, foreground and background processes, piping, I/O Redirection within command pipelines, autocomplete, signals, history, discover(recursive search for files withing directories emulating find command) along with handling of flags, etc.}
          \resumeItemListEnd 
        \vspace{-13pt}
        \resumeProjectHeading
          {\textbf{xv-6-riscv-evo} $|$ \emph{Assembly, Makefile, C, Git, Operating System Concepts}}{https://github.com/schlechter-afk/xv-6-riscv-evo}
          \resumeItemListStart
            \resumeItem{Collaborated on enhancing the original xv6-riscv OS by making modifications in the source code. Implemented syscalls: trace, sigalarm, sigreturn. Scheduling policies implemented: FirstComeFirstServe(FCFS), LotteryBased(LBS), PriorityBased(PBS), MultiLevelFeedbackQueue(MLFQ). Optimal memory resource management using Copy-On-Write fork implemented. Schedulers' performance comparison and analysis also done. }
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C++, C, HTML/CSS, JavaScript, SQL} \\
     \textbf{Technologies/Frameworks}{: Linux, Git, MongoDB, ExpressJS, ReactJS, NodeJS, ChartJS, Docker, Nginx, Flask, PHP, MySQL, Robot Operating System(ROS), PyTorch.} \\
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------INVOLVEMENT---------------
\section{Achievements / Extracurriculars}
    \resumeItemListStart
        \resumeItem{Merit List in College for excellent academic performance.}
        \resumeItem{Avid programmer, solving problems on coding platforms like Codeforces, Codechef, Atcoder etc. I maintain a list of my solutions to nice algoithmic problems on a variety of topics here: \href{https://github.com/schlechter-afk/competitive-programming}{\underline{\color{blue} github-repo}}. \href{https://codeforces.com/profile/Aegislash04}{\underline{\color{blue}Profile}}}
        \resumeItem{Active member of the Chess Club of IIIT Hyderabad.}
        \resumeItemListEnd

\end{document}
